---  
title: "R Notebook"
output: html_notebook
---

```{r libraries, echo=FALSE}
library(tidyverse)
library(ggplot2)
library(codingMatrices)
```

```{r}
cuhdata_dir = 'C:\\Users\\AdedayoAdeyomoye\\Documents\\School\\CAM\\MSt\\Dissertation\\References\\Data\\Analysis\\R'

```



#Full Data

```{r}
comorb_eth_los_file = paste0(cuhdata_dir, '\\', 'ITUCOMOREthXLos.csv') 
comorb_eth_los_dat_full = read.table(comorb_eth_los_file, sep=',', header = TRUE)
comorb_eth_los_dat_full_grp = comorb_eth_los_dat_full
comorb_eth_los_dat_full$Ethnicity = as.factor(comorb_eth_los_dat_full$Ethnicity)
head(comorb_eth_los_dat_full)
summary(comorb_eth_los_dat_full$Ethnicity)
```


#Relevant Data

```{r}
comorb_eth_los_dat = comorb_eth_los_dat_full[,c(2,3,4)]
head(comorb_eth_los_dat)


```

#Relevant Data

```{r}
comorb_eth_los_dat_grp = comorb_eth_los_dat_full_grp[,c(2,3,4)]
#comorb_eth_los_dat_grp$Ethnicity[(comorb_eth_los_dat$Ethnicity != 'A'), ]
#head(comorb_eth_los_dat_grp)
comorb_eth_los_dat_grp = comorb_eth_los_dat_grp[which(comorb_eth_los_dat_grp$Ethnicity != 'Z'), ]
comorb_eth_los_dat_grp$Ethnicity[which(comorb_eth_los_dat_grp$Ethnicity != 'A')] = 'X'
comorb_eth_los_dat_grp$Ethnicity=as.factor(comorb_eth_los_dat_grp$Ethnicity)
summary(comorb_eth_los_dat_grp$Ethnicity)
```
#Ethnicity GRP Vs LOS
```{r}

comorb_eth_los_dat_grp %>% ggplot(aes( x=Ethnicity, y=LOS, fill=Ethnicity )) + geom_boxplot() +labs(title = "Effect of Grouped Ethnicity on LOS") + theme(plot.title = element_text(hjust = 0.5, )) + theme(text=element_text(family="Calibri", face="bold", size=12))

```

#Average and IQR LOS per Ethnicity GRP
```{r} 
summary(comorb_eth_los_dat_grp[which(comorb_eth_los_dat_grp$Ethnicity == 'A'),2:3])

summary(comorb_eth_los_dat_grp[which(comorb_eth_los_dat_grp$Ethnicity == 'X'),2:3])
```

#Linear Model on Ethnicity GRP vs LOS
```{r}
com_fit = lm(LOS ~ Ethnicity, data=comorb_eth_los_dat_grp)
summary(com_fit)

```

#Average LOS by Comorbidities
```{r} 
summary(comorb_eth_los_dat[,2:3])
```

#Ethnicity vs LOS Data
```{r} 
eth_los_dat = comorb_eth_los_dat_full[,c(2,4)]
head(eth_los_dat)
```


#Average and IQR LOS for All Ethnicity
```{r}
summary(eth_los_dat[,1:2])

```

#Ethnicity Vs LOS
```{r}

comorb_eth_los_dat %>% ggplot(aes( x=Ethnicity, y=LOS, fill=Ethnicity )) + geom_boxplot() +labs(title = "Effect of Ethnicity on LOS") + theme(plot.title = element_text(hjust = 0.5, )) + theme(text=element_text(family="Calibri", face="bold", size=12))

```

#Average and IQR LOS per Ethnicity
```{r}
eths = c('A','B','C', 'F', 'G','K','L','M','N','R','S','Z')

print(eths[1])
summary(comorb_eth_los_dat[which(comorb_eth_los_dat$Ethnicity == eths[1]),2:3])

print(eths[2])
summary(comorb_eth_los_dat[which(comorb_eth_los_dat$Ethnicity == eths[2]),2:3])

print(eths[3])
summary(comorb_eth_los_dat[which(comorb_eth_los_dat$Ethnicity == eths[3]),2:3])

print(eths[4])
summary(comorb_eth_los_dat[which(comorb_eth_los_dat$Ethnicity == eths[4]),2:3])

print(eths[5])
summary(comorb_eth_los_dat[which(comorb_eth_los_dat$Ethnicity == eths[5]),2:3])

print(eths[6])
summary(comorb_eth_los_dat[which(comorb_eth_los_dat$Ethnicity == eths[6]),2:3])

print(eths[7])
summary(comorb_eth_los_dat[which(comorb_eth_los_dat$Ethnicity == eths[7]),2:3])

print(eths[8])
summary(comorb_eth_los_dat[which(comorb_eth_los_dat$Ethnicity == eths[8]),2:3])

print(eths[9])
summary(comorb_eth_los_dat[which(comorb_eth_los_dat$Ethnicity == eths[9]),2:3])

print(eths[10])
summary(comorb_eth_los_dat[which(comorb_eth_los_dat$Ethnicity == eths[10]),2:3])

print(eths[11])
summary(comorb_eth_los_dat[which(comorb_eth_los_dat$Ethnicity == eths[11]),2:3])

print(eths[12])
summary(comorb_eth_los_dat[which(comorb_eth_los_dat$Ethnicity == eths[12]),2:3])

```

#Number of Co-morbidities vs LOS BoxPlot
```{r}
comorb_eth_los_dat$Comorbiditiesf = as.factor(comorb_eth_los_dat$Comorbidities)

comorb_eth_los_dat %>% ggplot(aes( x=Comorbiditiesf, y=LOS, fill=Comorbiditiesf )) + geom_boxplot() +labs(title = "Co-morbidities vs LOS", x ="Co-morbidities",fill="Co-morbidities") + theme(plot.title = element_text(hjust = 0.5, )) + theme(text=element_text(family="Calibri", face="bold", size=12))

```

#Linear Model on Number of Co-morbidities vs LOS
```{r}
com_fit = lm(LOS ~ Comorbiditiesf, data=comorb_eth_los_dat)
summary(com_fit)

```

#Comorbidities vs LOS Diagnostics Plot     
```{r}

com_fit = lm(LOS ~ Comorbidities, data=comorb_eth_los_dat)
plot(com_fit)
head(comorb_eth_los_dat)

```


#Comorbidities vs LOS Regression Plot
```{r}
#plot(LOS ~ Comorbidities, data=comorb_eth_los_dat)
#abline(fit)

comorb_eth_los_dat %>% ggplot(aes(x=Comorbidities, y=LOS))+
  geom_point() +
  geom_smooth(method='lm', se = FALSE) +labs(title = "Effect of Co-morbidities on LOS Regression Plot", x="Co-morbidities") + theme(plot.title = element_text(hjust = 0.5))+ theme(text=element_text(family="Calibri", face="bold", size=12))
```


#Extracting Slope, and Importance of Intercept for Co-morbidities vs LOS
```{r}
summary(com_fit)
```

#Linear Model for Ethnicity vs LOS 
```{r}

eth_com_fit = lm(LOS ~ Ethnicity, data=comorb_eth_los_dat)
summary(eth_com_fit)

```
#Linear Model for Co-morbidities and Ethnicity Interaction vs LOS
```{r}

eth_com_fit = lm(LOS ~ Comorbidities + Ethnicity +  Comorbidities * Ethnicity, data=comorb_eth_los_dat)
summary(eth_com_fit)

```



#Comorbidities that significantly affect LOS Data
```{r}
prev_comorb_los_file = paste0(cuhdata_dir, '\\', 'PrevelentComobsLOS.csv') 
prev_comorb_los_dat_full = read.table(prev_comorb_los_file, sep=',', header = TRUE)
prev_comorb_los_dat_full$Comorbidities = as.factor(prev_comorb_los_dat_full$Comorbidities)
head(prev_comorb_los_dat_full)
#summary(prev_comorb_los_dat_full[which(prev_comorb_los_dat_full$merged_comorb_name == 'Anaemia'),])
summary(prev_comorb_los_dat_full)
```

#Common Prevalent Co-morbidities Box Plot
```{r} 
prev_comorb_los_dat_full %>% ggplot(aes(x=Comorbidities, y=LOS, fill=Comorbidities)) + geom_boxplot()+labs(title = "Common Prevalent Co-morbidities BoxPlot", x="Co-morbidities") + theme(plot.title = element_text(hjust = 0.5))+ theme(text=element_text(family="Calibri", face="bold", size=12)) + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
#Common Prevalent Co-morbidities Linear Model
```{r}  
prev_comorb_los_dat_full$Comorbidities = relevel(prev_comorb_los_dat_full$Comorbidities, ref = "COPD")
p_com_fit = lm(LOS ~ Comorbidities, data=prev_comorb_los_dat_full)
summary(p_com_fit)
```
