---  
title: "R Notebook"
output: html_notebook
---

```{r libraries, echo=FALSE}
library(tidyverse)
library(ggplot2)

```

```{r}
cuhdata_dir = 'C:\\Users\\AdedayoAdeyomoye\\Documents\\School\\CAM\\MSt\\Dissertation\\References\\Data\\Analysis\\R'

```



#Full Data

```{r}
comorb_eth_readmit_file = paste0(cuhdata_dir, '\\', 'ITUCOMOREthXReAdmit.csv') 
comorb_eth_readmit_dat_full = read.table(comorb_eth_readmit_file, sep=',', header = TRUE)
comorb_eth_readmit_dat_full$Ethnicity = as.factor(comorb_eth_readmit_dat_full$Ethnicity)
comorb_eth_readmit_dat_full$L_Readmission = as.factor(comorb_eth_readmit_dat_full$L_Readmission)
head(comorb_eth_readmit_dat_full)

```


#Relevant Data

```{r}
comorb_eth_readmit_dat = comorb_eth_readmit_dat_full[,c(2,3,4)]
head(comorb_eth_readmit_dat)


```

#Average Readmission by Comorbidities
```{r} 
summary(comorb_eth_readmit_dat[,2:3]) # This is to know the number of readmissions and non-readmissions
#loadfonts(device = "win")

```


#Readmission vs Comorbidities BoxPlot
```{r}
comorb_eth_readmit_dat %>% ggplot(aes(x=L_Readmission, y=Comorbidities, fill=L_Readmission)) + geom_boxplot() +labs(title = "Readmission vs Co-morbidities", x="Readmission", y="Co-morbidities ", fill="Readmission") + theme(plot.title = element_text(hjust = 0.5))+ theme(text=element_text(family="Calibri", face="bold", size=12))
```

#Appendix 11

```{r}

summary(comorb_eth_readmit_dat$Comorbidities[comorb_eth_readmit_dat$X_Readmission == 0])

summary(comorb_eth_readmit_dat$Comorbidities[comorb_eth_readmit_dat$X_Readmission == 1])

```


#Comorbidities vs Readmission Logistic Regression
```{r}

comorb_eth_readmit_fit = glm(L_Readmission ~ Comorbidities, family="binomial", data=comorb_eth_readmit_dat)
summary(comorb_eth_readmit_fit) 

```

#Co-morbidities vs Probability of Readmission Logistic Regression Plot
```{r}
 

model <- glm(L_Readmission ~ Comorbidities, data=comorb_eth_readmit_dat, family=binomial) 

#define new data frame that contains predictor variable
newdata <- data.frame(Comorbidities=seq(0, 40,len=500))

#use fitted model to predict values of vs
newdata$L_Readmission = predict(model, newdata, type="response")

#plot logistic regression curve
comorb_eth_readmit_dat$X_Readmission[as.integer(comorb_eth_readmit_dat$L_Readmission) == 1] = 0
comorb_eth_readmit_dat$X_Readmission[as.integer(comorb_eth_readmit_dat$L_Readmission) == 2] = 1

#view(comorb_eth_readmit_dat$X_Readmission )
plot(y=comorb_eth_readmit_dat$X_Readmission , x=comorb_eth_readmit_dat$Comorbidities , xlab = "Number of Co-morbidities", ylab = "Probability of Readmission", main = "Co-morbidities vs Probability of Readmission")
lines(y=newdata$L_Readmission, x=newdata$Comorbidities, lwd=2) 

#view(comorb_eth_readmit_dat$L_Readmission)
```

#Ethnicity vs Readmission Logistic Regression Model

```{r}
com_eth_readmit_fit = glm(L_Readmission ~ Ethnicity, family='binomial',data=comorb_eth_readmit_dat_full)
summary(com_eth_readmit_fit)

```


#Comorbidities and Ethnicity vs Readmission Logistic Regression Model

```{r}
com_eth_readmit_fit = glm(L_Readmission ~ Comorbidities + Ethnicity, family='binomial',data=comorb_eth_readmit_dat_full)
summary(com_eth_readmit_fit)

```

#Data - IQR for Prevalent Comorbidity on Readmission
```{r}

prev_comorb_readmit_file = paste0(cuhdata_dir, '\\', 'ITUSpecificCOMORXReadmit.csv') 
prev_comorb_readmit_dat_full = read.table(prev_comorb_readmit_file, sep=',', header = TRUE)
prev_comorb_readmit_dat_full$merged_comorb_name = as.factor(prev_comorb_readmit_dat_full$merged_comorb_name)
head(prev_comorb_readmit_dat_full)
#summary(prev_comorb_readmit_dat_full[which(prev_comorb_readmit_dat_full$merged_comorb_name == 'Anaemia'),])
summary(prev_comorb_readmit_dat_full)


```

#Significance of each Comorbidity on Readmission
```{r}
prev_comorb_readmit_dat_full$merged_comorb_name = relevel(prev_comorb_readmit_dat_full$merged_comorb_name, ref = "COPD")
prev_comorb_readmit_fit = glm(l_readmission ~ merged_comorb_name, family='binomial',data=prev_comorb_readmit_dat_full)
summary(prev_comorb_readmit_fit)


```



#Data for Co-morbidities vs Readmission Probability Geom-Bar
```{r} 
comorb_readmit_probabhs_file = paste0(cuhdata_dir, '\\', 'ITUSpecificCOMORXReadmitProbability.csv') 
comorb_readmit_probabhs_dat_full = read.table(comorb_readmit_probabhs_file, sep=',', header = TRUE)
#comorb_readmit_probabhs_dat_full$Comorbidities = as.factor(comorb_readmit_probabhs_dat_full$Comorbidities)
#comorb_readmit_probabhs_dat_full$Probability_Readmission = as.factor(comorb_readmit_probabhs_dat_full$Probability_Readmission)
head(comorb_readmit_probabhs_dat_full)

```

#Comorbidity on Readmission Probability Geom Bar
```{r} 
comorb_readmit_probabhs_dat_full %>% ggplot +geom_bar(aes(x= reorder(merged_comorb_name, Probability_Readmission), y=Probability_Readmission), fill = "purple",  stat="identity", position = "dodge")   + theme(plot.title = element_text(hjust = 0.5,))+ theme(text=element_text(family="Calibri", face="bold", size=12))+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) + coord_flip() +
  aes(y = after_stat(count)/sum(after_stat(count))) + 
  scale_y_continuous(labels = scales::percent)+labs(title = "Percentage Probability of Readmission by Co-morbidity", x="Co-morbidities", y="Probability of Readmission") 

```